Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
sync fine

langs <- c("Finnish", "Swedish", "Latin", "German", "French", "Russian", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0

dfl <- NULL

@@

# Calculate percentages
dff <- spread(df, language, n, fill = 0)
dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
dff <- gather(dff, publication_decade);
colnames(dff) <- c("publication_decade", "language", "f")
dff$language <- factor(dff$language, levels = langs)

>>>>

langs <- c("Finnish", "Swedish", "Latin", "German", "French", "Russian", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL

@@

# Calculate percentages
dff <- spread(df, language, n, fill = 0)
dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
#dff <- gather(dff, publication_decade);
dff <- melt(dff, "publication_decade");
colnames(dff) <- c("publication_decade", "language", "f")
dff$language <- factor(dff$language, levels = langs)
